\bf Focusing on Fast Neural Network Inference

### 2018-05-17 wnmt.2018/wnmt.tex
cast

\begin{algorithm}
\begin{algorithmic}
\Procedure{Batching}{encoded records $i$}

@@

\While{$b$ is not empty} 
  \State $b' \gets$ DecodeAndBeamSearch($b$)
  \State $b \gets \emptyset$

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|} \hline
		& \multicolumn{3}{|c|}{\emph{State dim}}	\\ \hline	
Vocab size	& 256	& 512	& 1024 \\ \hline
1000 		& 12.23 &	& 12.77 \\ 
5000		& 16.79	&  	& 17.16 \\ 
10,000		& 18.00	& 	& 18.19 \\
20,000		& -	&	& 19.52 \\ 
30,000		& 18.51	& 19.17	& 19.64 \\ \hline
\end{tabular}
\end{center}
\caption{Validation set BLEU (newstest2014) for GRU-based model}
\label{tab:BLEU for newstest2014}
\end{table}

@@

Using batching can increase the translation speed by over 20 times in Amun and shows little degradation with larger batch sizes, Figure~\ref{fig:batch-size}. This contrast with using the Marian, which uses a simpler batching algorithm, where the speedup is approximately 16 times and inference speed slows down when the batch size is above 1000.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batch size during decoding}
\label{fig:batch-size}
\end{figure}

The efficiency of Amun's batching algorithm can be seen by observing the time taken for each decoding step in a batch of sentence, Figure~\ref{fig:decode-step}. Amun's decoding becomes faster as sentences finish translating. By contrast, Marian's decoding time stays relatively constant.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{decode-step.png}} 
\end{tabular}
\caption{Time taken for decoding each for a batch of 1280 sentences}
\label{fig:decode-step}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batch size during decoding (Europarl test set)}
\label{fig:batch-size}
\end{figure}

>>>>

\begin{algorithm}
\begin{algorithmic}
\Procedure{Batching}{encoded sentences $i$}

@@

\While{$b \neq \emptyset$} 
  \State $b' \gets$ DecodeAndBeamSearch($b$)
  \State $b \gets \emptyset$

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|r|} \hline
		& \multicolumn{3}{|c|}{\emph{State dim}}	\\ \hline	
Vocab size	& 256	& 512	& 1024 \\ \hline
1.000 		& 12.23 &	& 12.77 \\ 
5,000		& 16.79	&  	& 17.16 \\ 
10,000		& 18.00	& 	& 18.19 \\
20,000		& -	&	& 19.52 \\ 
30,000		& 18.51	& 19.17	& 19.64 \\ \hline
\end{tabular}
\end{center}
\caption{Validation set BLEU (newstest2014) for GRU-based model}
\label{tab:BLEU for newstest2014}
\end{table}

@@

The efficiency of Amun's batching algorithm can be seen by observing the time taken for each decoding step in a batch of sentence, Figure~\ref{fig:decode-step}. Amun's decoding becomes faster as sentences finish translating. This contrast with the Marian inference engine, which uses a simpler batching algorithm, where the speed stays relatively constant throughout the decoding of the batch.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{decode-step.png}} 
\end{tabular}
\caption{Time taken for each decoding step for a batch of 1280 sentences}
\label{fig:decode-step}
\end{figure}

Using batching can increase the translation speed by over 20 times in Amun and shows little degradation with larger batch sizes, Figure~\ref{fig:batch-size}. Just as importantly, however, it doesn't suffer degradation with large batch sizes unlike the simpler algorithm which slows down when the batch size is above 1000. This scalability issue is likely to increase with ever increasing core counts.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Speed v. batch size}
\label{fig:batch-size}
\end{figure}

@@
